Apriori algorithm in R
==================

In this example I use data and functions from R package arules.Dataset used is a census income database. 
While this might not be most suitable for mining for interesting patterns, it still can be used as example. 
```{r warning=FALSE, message=FALSE}
require(arules)
data(Adult)
data(AdultUCI)
```


 
I used already preprocessed data Adult was already prepared and coerced to transactions class for use with  
arules package. 
In the following command I used apriori algorithm. I specified minimum support level to 0.5, minconfidence to 0.9 and I was only interested in rules of length at least of 4. 
```{r  warning=FALSE, message=FALSE, results='hide'} 
rules <- apriori(Adult,
                 parameter = list(supp = 0.5, conf = 0.9,minlen=4,
                                 target = "rules"))
```

```{r }
summary(rules)
```

We can inspect the rules with this command.
```{r}
inspect((sort(rules, by = "confidence")))
```

While we found some strong association rules, none of them are of interesting variety. This has to do more with this particular dataset, then a method being used. 
